---
title: "Developing Data Products Course Project 3"
subtitle: "Use the spacebar or arrow keys to navigate slides"
author: "Dustin Lanning"
date: "May 12, 2019"
output: 
  ioslides_presentation: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(plotly)
data("mtcars")
```

## The Project

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly.

The presentation must meet the following requirements:

*The web page must feature a date and the date must be less than two months before the date that you're grading this assignment

*The web page must be a presentation and it must feature an interactive plot that appears to have been created with Plotly.

## MTCars Scatterplot

```{r, echo=FALSE, warning=FALSE, message=FALSE}
plot_ly(mtcars, x = ~wt, y = ~mpg, mode = "markers", color = ~as.factor(cyl), size = ~hp)
```